|

### 2023-05-08 paper/01-introduction.Rmd
better section title

## Previous Pass-Rush Measure in academic literaure

The academic literature on the performance of linemen, either offensive or defensive in football is scant. @AlamarGould2008 studied the the relationship between pass completion rate and performance of offensive linemen in terms of how successful they were at blocking.  The data for this study was collecting essentially by hand by watching and charting the performance of each lineman on a play.  This was done using games from the beginning 2007 season for seven teams and their first three games each.  The authors note that there is not much research on linemen saying "One of the principal reasons for this lack of study is the absence of publicly available data that is needed in order to track the performance of a specific lineman."

>>>>

<!-- ## Previous Pass-Rush Measure in academic literaure -->

## Previous Research on Football Linemen

The literature on the performance of linemen, either offensive or defensive in football is scant. @AlamarGould2008 studied the the relationship between pass completion rate and performance of offensive linemen in terms of how successful they were at blocking.  The data for this study was collecting essentially by hand by watching and charting the performance of each lineman on a play.  This was done using games from the beginning 2007 season for seven teams and their first three games each.  The authors note that there is not much research on linemen saying "One of the principal reasons for this lack of study is the absence of publicly available data that is needed in order to track the performance of a specific lineman."
